Ceph Parallel File System Evaluation Report

### 2013-08-27 testbed.tex
add paper flow and organization into introduction
updated the tesbed description

\section{Testbed Environment Description}

We used Data Direct Networks' (DDN) SFA10K as the storage backend during this
evaluation. It consists of 200 SAS drives and 280 SATA drives, organized into
various RAID levels by two active-active RAID controllers. The exported RAID
groups by these controllers are driven by four hosts.
Each host has two InfiniBand (IB) QDR connections to the storage backend.
We used a single dualport Mellanox connectX IB card per host.
By our calculation, this setup can saturate SFA10K's maximum theoretical
throughput (\textasciitilde 12 GB/s). The connection diagram is illustrated in
Figure~\ref{fig:ddn-sfa10k}.

@@

Our Ceph testbed employs a collection of testing nodes. These nodes and their
roles are summarized in Table~\ref{tbl:ceph-test-nodes}. In the following
discussion, we use ``servers'', ``osd servers'', ``server hosts''
interchangably. We will emphasize with ``client'' prefix when we want to
distinguish it from above.

>>>>

\section{Testbed Environment Description}
\label{sec:testbed}

We used Data Direct Networks' (DDN) SFA10K as the storage backend for this
evaluation. SFA10K organizes disks into various RAID levels by two
active-active RAID controllers. The exported RAID groups (LUNs) by these
controllers are driven by four server hosts (oss-[1-4]).  Each server host has two InfiniBand
(IB) QDR connections to the storage backend.  We used a single dual-port
Mellanox ConnectX IB QDR card per host.  By our calculation, this setup is
adequate to drive the SFA10K at its maximum theoretical throughput (roughly 12
GB/s). Server hosts and SFA10K connection diagram is illustrated in
Figure~\ref{fig:ddn-sfa10k}.

@@

Our SFA10K system consists of 200 SAS drives and 280 SATA drives, hosted in a
10-tray configuration. Each DDN SA4601 disk tray can host up to 60 disks and
has two SAS links per controller (four in total). The SATA and SAS disks in our
testbed are distributed evenly over ten SA4601 disk trays (20 SAS and 28 SATA
disks per tray). Each SFA10K RAID controller has two RAID processors and each
RAID processor hosts a dual-port IB QDR card. The disks are organized into RAID
groups by the RAID processors (software RAID) and then exported to connected
server hosts over the IB connections. Since each DDN SFA10K controller is a
stand-alone computer system running Linux, CPU and memory affinity while
organizing disks into RAID groups and exporting them is crucial for obtaining
top performance out of an SFA10K system.

Our Ceph testbed employs a collection of nodes, including the server hosts
(oss-[1-4]). These nodes and their roles are summarized in
Table~\ref{tbl:ceph-test-nodes}. In the following discussion, we use
``servers'', ``osd servers'', ``server hosts'' interchangeably. We will
emphasize with ``client'' prefix when we want to distinguish it from above.
